RAX:Efficiently Evaluating the Complexity of Porting for RISC-V

### 2024-01-29 Paper/latex1-27/paper.tex
update

% \section{RAX}
% The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
% During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
% A scanning tool is built to get potential modification workload.
% Finally,an appropriate machine learning model is selected as a classification.
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure1.pdf}
%   \caption{Flow chart for method to build RAX}
%   \label{fig:figure1}
%   \Description{Flow chart for method to build RAX}
% \end{figure}
\section{Motivation}
We propose the following research questions:

\textbf{RQ 1:} How can we select architecture-relevant factors that is fine-grained to design an automated evaluation tool of porting complexity?

\textbf{RQ 2:} How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure2.pdf}
%   \caption{The relationship between score and CC}
%   \label{fig:figure2}
%   \Description{The relationship between score and CC}
% \end{figure}

To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
First,we try to use code complexity metrics to evaluate porting work.
The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code. Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The relationship between score and CC}
  \label{fig:figure2}
  \Description{The relationship between score and CC}
\end{figure}
\subsection{Factor 1: Cyclomatic Complex(CC)}
\label{sec:factor-1}
We use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
this section calculate the correlation coefficient using the Spearman Rank.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 projects adapted for RISC-V,collected from the OpenEuler list\citep{stage2023} and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0,5]$.
The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, the relationship of factors shown in Figure \ref{fig:figure2}.

>>>>

% \section{RAX}
% The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
% During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
% A scanning tool is built to get potential modification workload.
% Finally,an appropriate machine learning model is selected as a classification.
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure1.pdf}
%   \caption{Flow chart for method to build RAX}
%   \label{fig:figure1}
%   \Description{Flow chart for method to build RAX}
% \end{figure}
\section{Motivation}
\textcolor{red}{To help developers more accurately assess the complexity of C/C++ projects, we aim to answer the following research questions:}

\textbf{RQ 1:} How can we identify architecture-relevant important factors affecting porting efficiency?

\textbf{RQ 2:} \textcolor{red}{ How to implement fine-grained and automated tools to help developers accurately assess the complexity of their projects in real world. } \textcolor{blue}{How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?}
% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figure2.pdf}
%   \caption{The relationship between score and CC}
%   \label{fig:figure2}
%   \Description{The relationship between score and CC}
% \end{figure}
\textcolor{red}{As we all known, the metrics of projects complexity is influenced by many factors, such as XXX,XXX. To answer RQ 1, we introduce the code Cyclomatic Complexity(CC) and Arch\_code.}

\textcolor{blue}{To answer RQ 1, First, we try to use code complexity metrics to evaluate porting work.
The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty. By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code. Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The relationship between score and CC}
  \label{fig:figure2}
  \Description{The relationship between score and CC}
\end{figure}
\subsection{Factor 1: Cyclomatic Complex(CC)}
\label{sec:factor-1}
We use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
this section calculate the correlation coefficient using the Spearman Rank.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 projects adapted for RISC-V,collected from the OpenEuler list\citep{stage2023} and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0,5]$.
The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, the relationship of factors shown in Figure \ref{fig:figure2}.
